### 2015-04-18 usecase-combinatoric.tex
GLL edits

The gperftools tool from Google has gained popularity among some developers for
its high-performance thread-safe heap and its lite-weight profilers.  
Unfortunately, two issues made it difficult to maintain gperftools installations 
at LLNL.  First, gperftools is a C++ library.  Since C++ does not have standard 
ABI it needs to be re-built with each compiler and compiler version.  Second, 
building gperftools on atypical architectures (such as Blue Gene/Q) requires 
patches and a complicated configure lines that change with each compiler.  The 
first issue motivated application developers to try and maintain their own builds 
of gperftools that worked with their prefered compilers--a task that was made 
difficult by the second issue.

>>>>

The gperftools tool from Google has gained popularity among some developers for
its high-performance thread-safe heap and its lite-weight profilers.
Unfortunately, two issues made it difficult to maintain gperftools installations
at LLNL.  First, gperftools is a C++ library.  Since C++ does not have standard
ABI it needs to be re-built with each compiler and compiler version.  Second,
building gperftools on atypical architectures (such as Blue Gene/Q) requires
patches and a complicated configure line that change with each compiler.  The
first issue motivated application developers to try and maintain their own builds
of gperftools that worked with their prefered compilers--a task that was made
difficult by the second issue.

### 2015-04-18 usecase-policy.tex
GLL edits

While Spack can easily create a dozen installs of a package like MPILeaks across different compilers and MPI implementations, it can be difficult for an end-user to determine which of those dozen packages should be used with their application.  As discussed in Section~\ref{sec:envmodule}, environment modules are commonly used on supercomputer systems to solve this problem, and Spack allows the package administrator to automatically create module and dotkit files for packages Spack installs.

@@

It is also useful to specify how site-specific options for how packages should be built.  The correct configure line for building packages may be different across sites.  For example, the Spindle tool can have logging locations and security policies specified on its configure line.  Spack can make reasonable guesses about Spindle's proper configure line, but it can not created a customized installation for the site.  One way to solve this would be to edit the Spindle package description in Spack and manually change how configure is invoked.  This is not ideal, as the Spindle package description is part of the Spack source code, and modifying it makes it difficult to share spack versions and updates across sites.

>>>>

While Spack can easily create a dozen installations of a package like MPILeaks across different compilers and MPI implementations, it can be difficult for an end-user to determine which of those dozen packages should be used with their application.  As discussed in Section~\ref{sec:envmodule}, environment modules are commonly used on supercomputer systems to solve this problem, and Spack allows the package administrator to automatically create module and dotkit files for packages Spack installs.

@@

It is also useful to specify site-specific options for how packages should be built.  The correct configure line for building packages may be different across sites.  For example, the Spindle tool can have logging locations and security policies specified on its configure line.  Spack can make reasonable guesses about Spindle's proper configure line, but it cannot create a customized installation for the site.  One way to solve this would be to edit the Spindle package description in Spack and manually change how configure is invoked.  This is not ideal, as the Spindle package description is part of the Spack source code, and modifying it makes it difficult to share spack versions and updates across sites.
